### 2013-01-08 edupar-13/landslide.tex
clarify landslide-friendly test characteristics

% TODO: This paragraph can be removed if we're hurting for space
We also note that, in contrast with stress testing, Landslide works best with very small test cases. While a more conventional stress test achieves coverage by exercising many system calls (in parallel and/or in sequence), Landslide's coverage results from exploring the different scheduling possibilities that arise from a short sequence of system calls.
If Landslide were used when running a stress test, the resulting state space would be too large to explore feasibly.
Hence, when working with students, we provided a suite of four test programs, each no longer than 10 lines of code.

>>>>

% TODO: This paragraph can be removed if we're hurting for space
We also note that, in contrast with stress testing, Landslide works best with very small test cases. While a more conventional stress test achieves coverage by exercising many system calls (in parallel and/or in sequence), Landslide's coverage results from exploring the different scheduling possibilities that arise from a short sequence of system calls.
If Landslide were used when running a stress test, the resulting state space would be too large to explore feasibly.
Hence, when working with students, we provided a suite of four test programs, each no longer than 10 lines of code, but carefully written to bring about system call interactions known to be troublesome.
